---
title: "HW13"
author: '106022113'
date: "5/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1. Visualize how wieght  and acceleration are related to mpg
### a. Visualize how wieght moderate the relationship between acceleration and mpg
```{r}
auto <- read.table("auto-data.txt",header = FALSE, na.strings = "?", stringsAsFactors = F)
names(auto) <- c("mpg","cylinders","displacement","horsepower","weight","acceleration","model_year","origin","car_name")
cars_log <- with(auto, data.frame(log(mpg),log(cylinders),log(displacement),log(horsepower),log(weight),log(acceleration),model_year,origin))
```

#### i. Create two subsetss, one for light cars and one for heavy cars
```{r}
light_car <- subset(cars_log, log.weight. < log(mean(auto$weight)))
heavy_car <- subset(cars_log, log.weight. > log(mean(auto$weight)))
```    

#### ii. Create scatter plot of acceleration vs mpg
```{r}
library(dplyr)
library(ggplot2)
cars_log <- cars_log %>% mutate(weight_level = ifelse(log.weight.>= log(mean(auto$weight)),"heavy", "light"))
sctplt <- ggplot(data = cars_log, aes(x = log.acceleration., y=log.mpg., col = factor(weight_level)))+
  geom_point()
sctplt
```
#### iii. Draw two slopes of acceleration vs mpg over scatter plot
```{r}
sctplt+geom_smooth(method = lm,fullrange = TRUE)
```

### b. Report the full summaries of two regressions for light and heavy cars
```{r}
light_regr <- lm(data = light_car, log.mpg.~ log.weight. + log.acceleration. + model_year + factor(origin))
heavy_regr <- lm(data = heavy_car, log.mpg.~ log.weight. + log.acceleration. + model_year + factor(origin))
summary(light_regr)
summary(heavy_regr)
```

### c. Use intuition: what do you observe about the light v.s. heavy cars?

## Question 2. Using the cars_log data to test moderation
### a. Use tuition to state which might be a moderating versus independent variable

### b. Use various models to model the possible moderation for log.mpg
#### i.Report regression without any interaction
```{r}
full_regr <- lm(log.mpg.~ log.weight.+log.acceleration.+model_year+factor(origin),data = cars_log)
summary(full_regr)
```
#### ii. Report regression with interaction between weight and acceleration
```{r}
wei_acc_regr <-lm(log.mpg.~ log.weight.+log.acceleration.+log.weight.*log.acceleration.,data = cars_log)
summary(wei_acc_regr)
```

#### iii. Report regression with mean-centered interaction term
```{r}
log.weight.mc <- scale(cars_log$log.weight.,center = TRUE, scale = FALSE)
log.acc.mc <- scale(cars_log$log.acceleration.,center = TRUE,scale = FALSE)
log.mpg.mc <- scale(cars_log$log.mpg., center = TRUE, scale = FALSE)
mc_regr <- lm(log.mpg.mc~ log.acc.mc+log.weight.mc+log.acc.mc*log.weight.mc)
summary(mc_regr)
```

#### iv. Report regression with an orthogonalized interaction term
```{r}
wei_x_acc <- cars_log$log.weight.*cars_log$log.acceleration.
inter_regr <- lm(wei_x_acc~ cars_log$log.weight.+cars_log$log.acceleration.)
inter_orth <- inter_regr$residuals
summary(lm(log.mpg.~ log.weight.+log.acceleration.+inter_orth,data = cars_log))
```

### c. For each interaction above, what is the coorelation between interaction and multiplied variables?
#### raw
```{r}
raw1 <- cor(cars_log$log.weight.*cars_log$log.acceleration.,cars_log$log.weight.)
raw2 <- cor(cars_log$log.weight.*cars_log$log.acceleration.,cars_log$log.acceleration.)
```

#### mean-centered
```{r}
mean1 <- cor(log.acc.mc*log.weight.mc,log.weight.mc)[1,]
mean2 <- cor(log.acc.mc*log.weight.mc,log.acc.mc)[1,]
```

#### orthogonalized 
```{r}
orth1 <- cor(inter_orth, cars_log$log.weight.)
orth2 <- cor(inter_orth,cars_log$log.acceleration.)
```

```{r}
mat <- matrix(c(raw1,raw2,mean1,mean2,orth1,orth2),ncol = 2,byrow = TRUE)
rownames(mat) <- c("raw","mean-centered","orthogonalized")
colnames(mat) <- c("log.weight","log.acceleration")
round(mat,3)
```