---
title: "HW16"
author: '106022113'
date: "6/8/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1. Composite Path Models using PLS-PM
```{r}
sec <- read.csv("security_data_sem.csv")
library(seminr)
```
### a. Create a PLS path model using SEMinR
#### i. Measurement Model
```{r}
sec_mm <- constructs(
  composite("TRUST",multi_items("TRST",1:4)), ##1.
  composite("SEC",multi_items("PSEC",1:4)), ##2.
  composite("REP",multi_items("PREP",1:4)), ##3.
  composite("INV",multi_items("PINV",1:3)), ##4.
  composite("POL",multi_items("PPSS",1:3)),##5.
  composite("FAML","FAML1"),##6.
  interaction_term("REP","POL",method = orthogonal)##7.
)
```

#### ii. Structural Model
```{r}
sec_sm <- relationships(
  paths(from = c("REP","INV","POL","FAML","REP*POL"),to = "SEC"),
  paths(from = "SEC",to = "TRUST")
)
```

### b. Show Results
```{r}
sec_pls <- estimate_pls(data = sec,
                        measurement_model = sec_mm,
                        structural_model = sec_sm)
sec_report <- summary(sec_pls)
```

#### i.Plot estimated model
```{r}
plot(sec_pls)
```

#### ii. Weights and Loadings of Composites
```{r}
sec_report$weights
```
```{r}
sec_report$loadings
```

#### iii. Regression coefficients of path between factors
```{r}
sec_report$paths
```

### iv. Bootstrapped path coefficients: t-values, 95% CI
```{r}
boot_pls <- bootstrap_model(sec_pls,nboot = 1000)
summary(boot_pls)
```

## Question 2. Common-Factor Models using CB-SEM
### a. Create a common factor model using SEMinR
```{r}
sec_cf_mm <- constructs(
  reflective("TRUST",multi_items("TRST",1:4)), ##1.
  reflective("SEC",multi_items("PSEC",1:4)), ##2.
  reflective("REP",multi_items("PREP",1:4)), ##3.
  reflective("INV",multi_items("PINV",1:3)), ##4.
  reflective("POL",multi_items("PPSS",1:3)),##5.
  reflective("FAML","FAML1"),##6.
  interaction_term("REP","POL",method = orthogonal))##7.
```

### b. Show us the following results in table or figure formats
```{r}
sec_cf_pls <- estimate_cbsem(data = sec,
                             measurement_model = sec_cf_mm,
                             structural_model = sec_sm)
```

#### i.Plot a figure of the estimated model 
```{r}
plot(sec_cf_pls)
```

#### ii. Loadings of composites
```{r}
sec_cf_report <- summary(sec_cf_pls)
sec_cf_report$loadings
```

### iii.Regression coefficients of paths between factors, and their p-values
```{r}
sec_cf_report$paths
```